---
title: "4 Phenotypic cross differences"
author: "Peter Euclide"
date: "4/15/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggsci)
library(ggpubr)
library(knitr)
library(rstatix)

```



# Main 2-way ANOVA results

```{r}
biodat <- read.csv("./data/master_BioData_ranks_poSAL.csv")
BioDat1to3 <- read.csv("./data/F1-biochemical-lipid.csv")

BioDat1to3 <- BioDat1to3 %>% mutate(year = as.character(year))

tmpDatFat <- biodat %>%
  filter(year>2014,!sampling_date%in% c("5/27/2015", "5/28/2015")) %>% mutate(year = as.character(year))
tmpDatLenWt <- biodat %>%
  filter(!sampling_date%in% c("5/27/2015", "5/28/2015")) %>% mutate(year = as.character(year))




kable(tidy(aov(fat.dry ~ cross*year,BioDat1to3)), caption="fat 2012 to 2014")

kable(tidy(aov(fatmeter~cross*year, tmpDatFat)), caption="fat 2015 to 2019")

kable(tidy(aov(length_mm~cross*year, tmpDatLenWt)), caption="length")

kable(tidy(aov(weight_g~cross*year, tmpDatLenWt)), caption="weight")

```

### write tukey results for ALL analyses.

This script supersedes Tukey test run individually later in this script.

```{r}

write.csv(tidy(TukeyHSD(aov(fat.dry ~ cross*year,BioDat1to3))),"./Tukfat12-14.csv")
write.csv(tidy(TukeyHSD(aov(fatmeter~cross*year, tmpDatFat))),"./Tukfat15-19.csv")
write.csv(tidy(TukeyHSD(aov(length_mm~cross*year, tmpDatLenWt))),"./TukLen12-19.csv")
write.csv(tidy(TukeyHSD(aov(weight_g~cross*year, tmpDatLenWt))),"./TukWtfat12-19.csv")

```


# Lipid content 


```{r, fig.height=8}


ggqqplot(biodat %>% filter(year>2014, !sampling_date%in% c("5/27/2015", "5/28/2015")), "fatmeter", facet.by = c("year", "cross"))
#ggsave("qq_lipid.png")


ggplot(biodat %>% filter(year>2014,!sampling_date%in% c("5/27/2015", "5/28/2015")), aes(x = cross, y = fatmeter, fill= cross))+
  geom_boxplot(alpha =.9)+
  facet_wrap(~year)+
  theme_bw()+
  #scale_fill_discrete(name = "Dose", )
  scale_fill_jama(labels = c("Lean (F) x Lean (M)", "Lean (F) x Siscowet (M)", "Siscowet (F) x Lean (M)", "Siscowet (F) x Siscowet (M)"), guide =guide_legend(nrow =2))+
  labs(y = "Fatmeter Reading", x = "Cross")+
  theme(text=element_text(size = 16), legend.position = "bottom")
#ggsave("fat_boxplots.tiff", width = 8, height = 5)


```


__ANOVA test results for lipid content:__

```{r fat statistical tests - anova}
# ad_aov <- biodat %>%
#   filter(year>2014,!sampling_date%in% c("5/27/2015", "5/28/2015")) %>% 
#   do(tidy(aov(fatmeter ~ cross*as.factor(year)))) 
# 
# 
# 
# ad_aov

```


__Tukey HSD test results for lipid content:__

```{r fat statistical tests - tukey}
# TukHSD <- biodat %>%
#   filter(year>2014, !sampling_date%in% c("5/27/2015", "5/28/2015")) %>% 
#   do(tidy(TukeyHSD(aov(.$fatmeter ~ .$cross*as.factor(.$year),
#                  ))))
# 
# kable(TukHSD, format =  "simple", digits = 3)

```


```{r, include = F}




fat_plot <- ggplot(biodat %>% filter(year>2014,!sampling_date%in% c("5/27/2015", "5/28/2015")), aes(x = as.character(year), y = fatmeter, fill= cross))+
  geom_boxplot(alpha =.9, position=position_dodge(0.85))+
  #facet_wrap(~year)+
  theme_bw()+
  #scale_fill_discrete(name = "Dose", )
  scale_fill_jama(labels = c("Lean (F) x Lean (M)", "Lean (F) x Siscowet (M)", "Siscowet (F) x Lean (M)", "Siscowet (F) x Siscowet (M)"), guide =guide_legend(nrow =2))+
  labs(y = "Fatmeter Reading", x = "")+
  theme(text=element_text(size = 16), legend.position = "bottom")#+
  #geom_text(data=fat.summarized,aes(x=as.character(year),y=UQR,group = cross,label=groups),vjust=-0.3, position = position_dodge(.85), size = 3)


```


## Lipid years 1 - 3

```{r}
 


####### combined datasets
bdat1 <- biodat %>% filter(year>2014,!sampling_date%in% c("5/27/2015", "5/28/2015")) %>% select("year", "cross", "fatmeter") %>% mutate(year = as.character(year))
bdat2 <- BioDat1to3 %>% select("year", "cross", "fat.dry") %>% mutate(year = as.character(year))
colnames(bdat2) <- c("year", "cross", "fatmeter")

ggqqplot(BioDat1to3 %>% select("year", "cross", "fat.dry"), "fat.dry", facet.by = c("year", "cross"))
#ggsave("./qq_fat12-14.png")


bdat <- bind_rows(bdat2, bdat1)
#tukDat <- bind_rows(fat.summarized2, fat.summarized)
  
fat_plot3 <- ggplot(bdat, aes(x = as.character(year), y = fatmeter, fill= cross))+
  geom_boxplot(alpha = 0.9, position=position_dodge(.85), outlier.shape = 1, geom = 'linerange', colour = "gray")+
  geom_boxplot(aes(ymin=..lower.., ymax=..upper..), alpha = 0.9, position=position_dodge(.85), outlier.shape = 1)+    geom_vline(xintercept=3.5, color="red", size=1, linetype = 2)+
  #facet_wrap(~year)+
  theme_bw()+
  #scale_fill_discrete(name = "Dose", )
  scale_fill_jama(labels = c("Lean (F) x Lean (M)", "Lean (F) x Siscowet (M)", "Siscowet (F) x Lean (M)", "Siscowet (F) x Siscowet (M)"), guide =guide_legend(nrow =2))+
  labs(y = "Lipid Content", x = "")+
  theme(text=element_text(size = 16), legend.position = "bottom")#+
  #geom_text(data=tukDat,aes(x=as.character(year),y=UQR,group = cross,label=groups),vjust=-0.3,hjust=-.15, position = position_dodge(.85), size = 3)  
  
```


# Length (mm)


```{r length, fig.height=8}



ggqqplot(biodat %>% filter(!sampling_date%in% c("5/27/2015", "5/28/2015")), "length_mm", facet.by = c("year", "cross"), scales="free")
#ggsave("C:/Users/peuclide/OneDrive - purdue.edu/UWSP_Larson_2018/projects/Lake_trout/ME_REVISIONS/qq_len.png")


ggplot(biodat %>% filter(!sampling_date%in% c("5/27/2015", "5/28/2015")), aes(x = cross, y = length_mm, fill= cross))+
  geom_boxplot()+
  facet_wrap(~year, scales = "free")+
  theme_bw()+
  #scale_fill_discrete(name = "Dose", )
  scale_fill_jama(labels = c("Lean (F) x Lean (M)", "Lean (F) x Siscowet (M)", "Siscowet (F) x Lean (M)", "Siscowet (F) x Siscowet (M)"), guide =guide_legend(nrow =2))+
  labs(y = "Length (mm)", x = "Cross")+
  theme(text=element_text(size = 16), legend.position = "bottom")


Len_plot <- ggplot(biodat %>% filter(!sampling_date%in% c("5/27/2015", "5/28/2015")), aes(x = as.character(year), y = length_mm, fill= cross))+
  geom_boxplot()+
  #facet_wrap(~year, scales = "free")+
  theme_bw()+
  #scale_fill_discrete(name = "Dose", )
  scale_fill_jama(labels = c("Lean (F) x Lean (M)", "Lean (F) x Siscowet (M)", "Siscowet (F) x Lean (M)", "Siscowet (F) x Siscowet (M)"), guide =guide_legend(nrow =2))+
  labs(y = "Length (mm)", x = "Cross")+
  theme(text=element_text(size = 16), legend.position = "bottom")



```



__ANOVA test results for length (mm):__

```{r length statistical tests - anova}
# ad_aov <- biodat %>%
#   filter(!sampling_date%in% c("5/27/2015", "5/28/2015")) %>% 
#   #group_by(year) %>% 
#   do(tidy(aov(.$length_mm ~ .$cross*as.factor(.$year)
#                  )))
# 
# kable(ad_aov, digits = 3,format =  "simple")

```

__Tukey HSD test results for length (mm):__


```{r length statistical tests - tukey}
# TukHSD <- biodat %>%
#   filter(!sampling_date%in% c("5/27/2015", "5/28/2015")) %>% 
#   #group_by(year) %>% 
#   do(tidy(TukeyHSD(aov(.$length_mm ~ .$cross*as.factor(.$year)
#                  ))))
# 
# 
# kable(TukHSD, digits = 3,format =  "simple")

```

```{r, include = F}



len_plot <- ggplot(biodat %>% filter(!sampling_date%in% c("5/27/2015", "5/28/2015")), aes(x = as.character(year), y = length_mm, fill= cross))+
  geom_boxplot(alpha = 0.9, position=position_dodge(.85), outlier.shape = 1, geom = 'linerange', colour = "gray")+
  geom_boxplot(aes(ymin=..lower.., ymax=..upper..), alpha = 0.9, position=position_dodge(.85), outlier.shape = 1)+  #facet_wrap(~year, scales = "free")+
  theme_bw()+
  #scale_fill_discrete(name = "Dose", )
  scale_fill_jama(labels = c("Lean (F) x Lean (M)", "Lean (F) x Siscowet (M)", "Siscowet (F) x Lean (M)", "Siscowet (F) x Siscowet (M)"), guide =guide_legend(nrow =2))+
  labs(y = "Length (mm)", x = "")+
  theme(text=element_text(size = 16), legend.position = "bottom")#+
  #geom_text(data=len.summarized,aes(x=as.character(year),y=UQR,group = cross,label=groups),vjust=-0.3, hjust = -.15, position = position_dodge(.85), size = 3)
  #geom_text(data=K.summarized,aes(x=as.character(year),y=UQR,group = cross,label=groups),vjust=-0.3, position = position_dodge2(1))+
  # annotate("text",x = .6, y = .9, label = "c")+
  # annotate("text",x = .6+.25, y = .9, label = "c")+
  # annotate("text",x = .6+.25+.25, y = .95, label = "c")


len_plot

```


# Weight (g)


```{r weight, fig.height=8}



ggqqplot(biodat %>% filter(!sampling_date%in% c("5/27/2015", "5/28/2015")), "weight_g", facet.by = c("year", "cross"), scales="free")
#ggsave("./qq_wt.png")



ggplot(biodat %>% filter(!sampling_date%in% c("5/27/2015", "5/28/2015")), aes(x = cross, y = weight_g, fill= cross))+
  geom_boxplot()+
  facet_wrap(~year, scales = "free")+
  theme_bw()+
  #scale_fill_discrete(name = "Dose", )
  scale_fill_jama(labels = c("Lean (F) x Lean (M)", "Lean (F) x Siscowet (M)", "Siscowet (F) x Lean (M)", "Siscowet (F) x Siscowet (M)"), guide =guide_legend(nrow =2))+
  labs(y = "Weight (g)", x = "Cross")+
  theme(text=element_text(size = 16), legend.position = "bottom")


Wt_plot <- ggplot(biodat %>% filter(!sampling_date%in% c("5/27/2015", "5/28/2015")), aes(x = as.character(year), y = weight_g, fill= cross))+
  geom_boxplot()+
  #facet_wrap(~year, scales = "free")+
  theme_bw()+
  #scale_fill_discrete(name = "Dose", )
  scale_fill_jama(labels = c("Lean (F) x Lean (M)", "Lean (F) x Siscowet (M)", "Siscowet (F) x Lean (M)", "Siscowet (F) x Siscowet (M)"), guide =guide_legend(nrow =2))+
  labs(y = "Weight (g)", x = "Cross")+
  theme(text=element_text(size = 16), legend.position = "bottom")



```



__ANOVA test results for Weight (g):__

```{r wt statistical tests - anova}
# ad_aov <- biodat %>%
#   filter(!sampling_date%in% c("5/27/2015", "5/28/2015")) %>% 
#   #group_by(year) %>% 
#   do(tidy(aov(.$weight_g ~ .$cross*as.factor(.$year)
#                  )))
# 
# kable(ad_aov, digits = 3,format =  "simple")

```

__Tukey HSD test results for Weight (g):__


```{r wt statistical tests - tukey}
# TukHSD <- biodat %>%
#   filter(!sampling_date%in% c("5/27/2015", "5/28/2015")) %>% 
#   #group_by(year) %>% 
#   do(tidy(TukeyHSD(aov(.$weight_g ~ .$cross*as.factor(.$year)
#                  ))))
# 
# 
# kable(TukHSD, digits = 3,format =  "simple")

```

```{r, include = F}



Wt_plot <- ggplot(biodat %>% filter(!sampling_date%in% c("5/27/2015", "5/28/2015")), aes(x = as.character(year), y = weight_g, fill= cross))+
  geom_boxplot(alpha = 0.9, position=position_dodge(.85), outlier.shape = 1, geom = 'linerange', colour = "gray")+
  geom_boxplot(aes(ymin=..lower.., ymax=..upper..), alpha = 0.9, position=position_dodge(.85), outlier.shape = 1)+  #facet_wrap(~year, scales = "free")+
  theme_bw()+
  #scale_fill_discrete(name = "Dose", )
  scale_fill_jama(labels = c("Lean (F) x Lean (M)", "Lean (F) x Siscowet (M)", "Siscowet (F) x Lean (M)", "Siscowet (F) x Siscowet (M)"), guide =guide_legend(nrow =2))+
  labs(y = "Weight (g)", x = "Year")+
  theme(text=element_text(size = 16), legend.position = "bottom")#+
  #geom_text(data=wt.summarized,aes(x=as.character(year),y=UQR,group = cross,label=groups),vjust=-0.3, hjust = -.15, position = position_dodge(.85),  size = 3)
  #geom_text(data=K.summarized,aes(x=as.character(year),y=UQR,group = cross,label=groups),vjust=-0.3, position = position_dodge2(1))+
  # annotate("text",x = .6, y = .9, label = "c")+
  # annotate("text",x = .6+.25, y = .9, label = "c")+
  # annotate("text",x = .6+.25+.25, y = .95, label = "c")


Wt_plot

```


# Condition Factor


```{r condition factor, fig.height=8}

### KTL  = 100000W/L3

biodat <- biodat %>% mutate(K = 100000*weight_g/length_mm^3)

ggqqplot(biodat %>% filter(!sampling_date%in% c("5/27/2015", "5/28/2015")), "K", facet.by = c("year", "cross"), scales="free")



ggplot(biodat %>% filter(!sampling_date%in% c("5/27/2015", "5/28/2015")), aes(x = cross, y = K, fill= cross))+
  geom_boxplot()+
  facet_wrap(~year, scales = "free")+
  theme_bw()+
  #scale_fill_discrete(name = "Dose", )
  scale_fill_jama(labels = c("Lean (F) x Lean (M)", "Lean (F) x Siscowet (M)", "Siscowet (F) x Lean (M)", "Siscowet (F) x Siscowet (M)"), guide =guide_legend(nrow =2))+
  labs(y = "Condition factor (K)", x = "Cross")+
  theme(text=element_text(size = 16), legend.position = "bottom")


K_plot <- ggplot(biodat %>% filter(!sampling_date%in% c("5/27/2015", "5/28/2015")), aes(x = as.character(year), y = K, fill= cross))+
  geom_boxplot()+
  #facet_wrap(~year, scales = "free")+
  theme_bw()+
  #scale_fill_discrete(name = "Dose", )
  scale_fill_jama(labels = c("Lean (F) x Lean (M)", "Lean (F) x Siscowet (M)", "Siscowet (F) x Lean (M)", "Siscowet (F) x Siscowet (M)"), guide =guide_legend(nrow =2))+
  labs(y = "Condition factor (K)", x = "Cross")+
  theme(text=element_text(size = 16), legend.position = "bottom")



```



__ANOVA test results for condition factor:__

```{r K statistical tests - anova}
# ad_aov <- biodat %>%
#   filter(!sampling_date%in% c("5/27/2015", "5/28/2015")) %>% group_by(year) %>% 
#   do(tidy(aov(.$K ~ .$cross,
#                  )))
# 
# kable(ad_aov, digits = 3,format =  "simple")

```

__Tukey HSD test results for condition factor:__


```{r K statistical tests - tukey}
# TukHSD <- biodat %>%
#   filter(!sampling_date%in% c("5/27/2015", "5/28/2015")) %>% group_by(year) %>% 
#   do(tidy(TukeyHSD(aov(.$K ~ .$cross,
#                  ))))
# 
# 
# kable(TukHSD, digits = 3,format =  "simple")

```

```{r, include = F}

TukHSD_dat <- biodat %>%
  filter(year>2011, !sampling_date%in% c("5/27/2015", "5/28/2015"))


years=unique(TukHSD_dat$year)
dat=data.frame(cross=as.character(), K=as.numeric(), groups=as.character())
for(y in years) {
  hsd=agricolae::HSD.test(aov(K ~ cross+year, data = TukHSD_dat[TukHSD_dat$year == y,]),trt= c("cross"), group=T)
  hsdGrp <- hsd$groups %>% rownames_to_column(var="cross") %>% mutate(year = y)
  dat <- bind_rows(dat, hsdGrp)
  
}
  

K.summarized = biodat %>% filter(year>2011,!sampling_date%in% c("5/27/2015", "5/28/2015")) %>%  group_by(cross, year) %>% summarize(UQR=quantile(K, .75, na.rm = T)) %>% left_join(.,dat, by = c("year", "cross"))



K_plot <- ggplot(biodat %>% filter(!sampling_date%in% c("5/27/2015", "5/28/2015")), aes(x = as.character(year), y = K, fill= cross))+
  geom_boxplot(alpha = 0.9, position=position_dodge(.85), outlier.shape = 1, geom = 'linerange', colour = "gray")+
  geom_boxplot(aes(ymin=..lower.., ymax=..upper..), alpha = 0.9, position=position_dodge(.85), outlier.shape = 1)+
  #facet_wrap(~year, scales = "free")+
  theme_bw()+
  #scale_fill_discrete(name = "Dose", )
  scale_fill_jama(labels = c("Lean (F) x Lean (M)", "Lean (F) x Siscowet (M)", "Siscowet (F) x Lean (M)", "Siscowet (F) x Siscowet (M)"), guide =guide_legend(nrow =2))+
  labs(y = "Condition factor (K)", x = "Year")+
  theme(text=element_text(size = 16), legend.position = "bottom")+
  geom_text(data=K.summarized,aes(x=as.character(year),y=UQR,group = cross,label=groups),vjust=-0.3, hjust = -.15, position = position_dodge(.85))
  #geom_text(data=K.summarized,aes(x=as.character(year),y=UQR,group = cross,label=groups),vjust=-0.3, position = position_dodge2(1))+
  # annotate("text",x = .6, y = .9, label = "c")+
  # annotate("text",x = .6+.25, y = .9, label = "c")+
  # annotate("text",x = .6+.25+.25, y = .95, label = "c")


K_plot

```



```{r Figure 1, fig.height=10, fig.width=8}

# fats <- ggarrange(fat_plot2, fat_plot, legend = "none", nrow =1, ncol = 2, widths = c(1,3))


ggarrange(fat_plot3, len_plot,Wt_plot, common.legend = T, nrow =3, ncol = 1, labels = c("A", "B", "C"))
#ggsave("ME_REVISIONS/Fig1.tiff", width = 8, height = 10)
#ggsave("ME_REVISIONS/Fig1.pdf", width = 8, height = 10)


#ggsave("C:/Users/peuclide/OneDrive - UWSP/UWSP_Larson_2018/projects/Lake_trout/Figures/Fig1c.tiff", width = 8)


```

# Growth

```{r, fig.height=8}
library(FSA)
library(nlstools)
library(car)
library(ggplot2)

# get sex for each individual

vb_data <- biodat %>% select(cross, SampleID, year, length_mm) %>% mutate(age = as.numeric(as.factor(year)))
vb_data <- drop_na(vb_data)

ggplot(vb_data, aes(x = age, y = length_mm, color = cross))+
  geom_point()+
  facet_wrap(~cross)+
  theme_bw()+
  scale_color_jama(labels = c("Lean (F) x Lean (M)", "Lean (F) x Siscowet (M)", "Siscowet (F) x Lean (M)", "Siscowet (F) x Siscowet (M)"), guide =guide_legend(nrow =2))+
  theme(legend.position = "bottom")


ll_starts <- vbStarts(length_mm~age, data= vb_data %>% filter(cross == "LxL"))
ls_starts <- vbStarts(length_mm~age, data= vb_data %>% filter(cross == "LxS"))
sl_starts <- vbStarts(length_mm~age, data= vb_data %>% filter(cross == "SxL"))
ss_starts <- vbStarts(length_mm~age, data= vb_data %>% filter(cross == "SxS"))

## fit model
vbTypical <- length_mm~Linf*(1-exp(-K*(age-t0)))

fitTypical_ll <- nls(vbTypical,data=vb_data %>% filter(cross == "LxL"),start=ll_starts)
fitTypical_ls <- nls(vbTypical,data=vb_data %>% filter(cross == "LxS"),start=ls_starts)
fitTypical_sl <- nls(vbTypical,data=vb_data %>% filter(cross == "SxL"),start=sl_starts)
fitTypical_ss <- nls(vbTypical,data=vb_data %>% filter(cross == "SxS"),start=ss_starts)

# bootstrap confidence intervals

bootTypical_ll <- nlsBoot(fitTypical_ll, niter=999)
bootTypical_ls <- nlsBoot(fitTypical_ls, niter=999)
bootTypical_sl <- nlsBoot(fitTypical_sl, niter=999)
bootTypical_ss <- nlsBoot(fitTypical_ss, niter=999)

```

## LxL Growth

```{r}

tidy(fitTypical_ll)

confint(bootTypical_ll, plot=T)



```

## LxS Growth

```{r}

tidy(fitTypical_ls)

confint(bootTypical_ls, plot=T)

```

## SxL Growth

```{r}

tidy(fitTypical_sl)

confint(bootTypical_sl, plot=T)

```

## SxS Growth

```{r}

tidy(fitTypical_ss)

confint(bootTypical_ss, plot=T)

```


```{r}
library(ggridges)

combined_Boot <- rbind(data.frame(bootTypical_ll$coefboot) %>% mutate(cross = "LxL"), 
                       data.frame(bootTypical_ls$coefboot) %>% mutate(cross = "LxS"),
                       data.frame(bootTypical_sl$coefboot) %>% mutate(cross = "SxL"),
                       data.frame(bootTypical_ss$coefboot) %>% mutate(cross = "SxS"))


Linf_p <- ggplot(combined_Boot, aes(x=Linf, y = cross, fill =cross))+
  geom_density_ridges(bandwidth=1)+
scale_fill_jama(labels = c("Lean (F) x Lean (M)", "Lean (F) x Siscowet (M)", "Siscowet (F) x Lean (M)", "Siscowet (F) x Siscowet (M)"), guide =guide_legend(nrow =2))+
  theme_bw()+
  xlab(expression("L"~infinity))+
  theme(legend.position = "bottom")

K_p <- ggplot(combined_Boot, aes(x=K, y = cross, fill =cross))+
  geom_density_ridges(bandwidth = 0.0025)+
  scale_fill_jama(labels = c("Lean (F) x Lean (M)", "Lean (F) x Siscowet (M)", "Siscowet (F) x Lean (M)", "Siscowet (F) x Siscowet (M)"), guide =guide_legend(nrow =2))+
  theme_bw()+
  theme(legend.position = "bottom")
 

t0_p <- ggplot(combined_Boot, aes(x=t0, y = cross, fill =cross))+
  geom_density_ridges(bandwidth=0.005)+
scale_fill_jama(labels = c("Lean (F) x Lean (M)", "Lean (F) x Siscowet (M)", "Siscowet (F) x Lean (M)", "Siscowet (F) x Siscowet (M)"), guide =guide_legend(nrow =2))+
  theme_bw()+
  theme(legend.position = "bottom")

VB_stats <- ggarrange(Linf_p, K_p, t0_p, common.legend = T, ncol=3, nrow=1, legend = "bottom", labels = c("B", "C", "D"))

```



## Combined Von B growth curves

this section is run interactively and requiiies users to follow documentation for the FSA package.

http://derekogle.com/fishR/examples/oldFishRVignettes/VonBertalanffy.pdf

```{r}

#predict2 <- function(x) predict(x,data.frame(age=ages))
#ages <- seq(-1,10,by=0.2)
#
#
#x <- fitTypical_ll
#predict3 <- function(x){
#  f.boot2 <- Boot(x,f=predict2)
#  preds1 <- data.frame(ages,
#                     predict(x,data.frame(age=ages)),
#                     confint(f.boot2))
#  names(preds1) <- c("age","fit","LCI","UCI")
#  preds1
#}
#
#f.boot_ll <- predict3(fitTypical_ll)
#f.boot_ls <- predict3(fitTypical_ls)
#f.boot_sl <- predict3(fitTypical_sl)
#f.boot_ss <- predict3(fitTypical_ss)
#
#xx=Boot(fitTypical_ll,f=predict2)
#preds1 <- data.frame(ages,
#                     predict(fitTypical_ll,data.frame(age=ages)),
#                     confint(xx))
#
## preds1 <- data.frame(ages,
##                      predict(fitTypical_ll,data.frame(age=ages)),
##                      confint(f.boot2))
## names(preds1) <- c("age","fit","LCI","UCI")
#
## LL_plot <- ggplot() + 
##   geom_ribbon(data=f.boot_ll %>% #filter(age>=0&age<=9),aes(x=age,ymin=LCI,ymax=UCI),fill="red")+
##   geom_point(data=vb_data %>% filter(cross == "LxL"), aes(y = length_mm, x=age))
## 
## LS_plot <- ggplot() + 
##   geom_ribbon(data=f.boot_ls %>% #filter(age>=0&age<=9),aes(x=age,ymin=LCI,ymax=UCI),fill="firebrick")+
##   geom_point(data=vb_data %>% filter(cross == "LxS"), aes(y = length_mm, x=age))
## 
## SL_plot <- ggplot() + 
##   geom_ribbon(data=f.boot_sl %>% #filter(age>=0&age<=9),aes(x=age,ymin=LCI,ymax=UCI),fill="blue")+
##   geom_point(data=vb_data %>% filter(cross == "SxL"), aes(y = length_mm, x=age))
## 
## SS_plot <- ggplot() + 
##   geom_ribbon(data=f.boot_ss %>% #filter(age>=0&age<=9),aes(x=age,ymin=LCI,ymax=UCI),fill="steelblue")+
##   geom_point(data=vb_data %>% filter(cross == "SxS"), aes(y = length_mm, x=age))
## 
## ggarrange(LL_plot, LS_plot, SL_plot, SS_plot)
#
#
#mypalJama = pal_jama("default", alpha = 0.7)(7)
#
#VB_p <- ggplot() + 
#  geom_ribbon(data=f.boot_ll %>% #filter(age>=0&age<=9),aes(x=age,ymin=LCI,ymax=UCI),fill="#374E55B2")+
#  geom_ribbon(data=f.boot_ls %>% #filter(age>=0&age<=9),aes(x=age,ymin=LCI,ymax=UCI),fill="#DF8F44B2")+
#  geom_ribbon(data=f.boot_sl %>% #filter(age>=0&age<=9),aes(x=age,ymin=LCI,ymax=UCI),fill="#00A1D5B2")+
#  geom_ribbon(data=f.boot_ss %>% #filter(age>=0&age<=9),aes(x=age,ymin=LCI,ymax=UCI),fill="#B24745B2")+
#  labs(x = "Age", y = "Length (mm)")+
#  scale_x_continuous(breaks=c(0:9))+
#  theme_bw()
#

```


```{r Figure 2, fig.width=8, fig.height=8}

#ggarrange(VB_p, VB_stats, nrow = 2, ncol = 1, labels = "A", label.x = 0)
#ggsave("C:/Users/peuclide/OneDrive - #UWSP/UWSP_Larson_2018/projects/Lake_trout/Figures/Growth_figure.tiff")

```


